Scheeper's Meager-NWD Game and the Menger Game

### 2014-04-28 phd/dissertation/chapter5.tex
Initial dissertation commit

\input{../header.tex}

\begin{document}

  \centerline{Menger}

@@

  % \begin{definition}
  %   A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
  % \end{definition}

  % \begin{proposition}
  %   For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
  % \end{proposition}

  % \begin{proof}
  %   The backward implication is trivial, so let $X$ be $H$-closed. For any open cover $\mc U$ of $X$ and point $x\in X$, choose $x\in V_x\subseteq \cl{V_x}\subseteq U_x\in \mc U$. Then if $\mc F = \{V_{x_i}:i<n\}$ is a finite subset of $\mc V=\{V_x:x\in X\}$ with dense union in $X$, then $\mc G = \{U_{x_i}:i<n\}\subseteq \mc U$ is a finite subcover of $X$.
  % \end{proof}

@@

  \begin{definition}
    A space suggested by G: Give $\kappa^\sharp=(\kappa\times\oneptlind\kappa)\cup\{\infty\}$ the topology where $\{\alpha\}\times\kappa^\sharp$ is an open copy of $\oneptlind{\kappa}$, and neighborhoods of $\infty$ contain a set of the form $\kappa^\sharp\setminus(A\times\oneptlind\kappa)$ for some $A\in[\kappa]^\omega$.
  \end{definition}

  \begin{theorem}
    $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
  \end{theorem}

  \begin{proof}
    Let $f_\alpha:\alpha\to\omega$ witness $S(\omega_1,\omega,\omega)$ for limit ordinals $\alpha<\omega_1$. Also note that there is a bijection $e:\omega_1\to[\omega_1]^{<\omega}$ such that $e\rest\alpha:\alpha\to[\alpha]^{<\omega}$ is also a bijection for each limit ordinal $\alpha<\omega_1$.

    We define the finite set $F(\alpha_n,\alpha_{n+1},n+1)$ to contain $e(\beta)$ for each $\beta<\alpha_n\cap\alpha_{n+1}$ such that either $f_{\alpha_{n+1}}(\beta)\leq n$ or $f_{\alpha_{n}}(\beta)\not=f_{\alpha_{n+1}}(\beta)$.

    If $\alpha_n<\omega_1$ for all $n<\omega$ with $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $G\in[\alpha]^{<\omega}$, note that for each $\beta<\alpha$, either $f_{\alpha_n}(\beta)=N$ always, or $f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)$ for some $n$. Either way, $e(\beta)\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$, and thus every finite subset of $\alpha$ is contained in some $F(\alpha_n,\alpha_{n+1},n+1)$.

    If we let $R(\alpha)=\omega_1^\sharp\setminus(A\times\oneptlind\omega_1)$ and $U(\gamma,\alpha)=\{\gamma\}\times(\oneptlind\omega_1\setminus\alpha)$, then any open cover of $\omega_1^\sharp$ may be refined to be of the form $\mc U_\alpha = \{R(\alpha)\}\cup\{U(\gamma,\alpha):\gamma<\alpha\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta<\alpha\}$ for some limit $\alpha$.

    Without loss of generality assume $\pl C$ plays only covers of the form $\mc U_\alpha$ for limit $\alpha$. Then we may define the $2$-Markov strategy $\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ to cover the sets:
      \[
        R(\alpha_{n+1})
      \]
      \[
        \bigcup \{U(\gamma,\alpha_{n+1}) : \gamma \in F(\alpha_n,\alpha_{n+1},n+1) \}
      \]
      \[
        \{(\gamma,\delta): \gamma,\delta\in F(\alpha_n,\alpha_{n+1},n+1)\}
      \]

    Let $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$ be an attack by $\pl C$, $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $\alpha'=\sup\{\alpha_{n+1}:n<\omega\}$. Since $\infty\in R(\alpha_0)$ always, first consider $(\gamma,\infty)$ for $\gamma<\omega_1$. If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\infty)\in R(\alpha_{n+1})$. Otherwise, $\gamma<\alpha$, but then $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\infty)\in U(\gamma,\alpha_{n+1})$.

    Lastly consider $(\gamma,\delta)$ for $\gamma,\delta<\omega_1$. If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\delta)\in R(\alpha_{n+1})$.

    Otherwise, $\gamma<\alpha$. If $\delta\geq \alpha'$, then as $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ we see $(\gamma,\delta)\in U(\gamma,\alpha_{n+1})$. If $\delta<\alpha$, then $\{\gamma,\delta\}\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\delta)$ is covered. The final case is when $\alpha\leq\delta<\alpha'$.

    (STILL MISSING STUFF)

    % If $\alpha_{n+1}=\beta$ is fixed for $n\in W\in[\omega]^\omega$, observe that $f_{\alpha_{n+1}}(\gamma)=f_\beta(\gamma)=N$ for all $n\in W$, and thus $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n\in W\setminus N$. Thus $(\gamma,\delta)\in U(\gamma,\alpha)$ is covered.
  \end{proof}

  % \begin{lemma}
  %   For each infinite cardinal $\kappa$, the sentence $S(\kappa,\omega,\omega)$ implies there exists a function $F:[\kappa]^\omega\times[\kappa]^\omega\times\omega\to [\kappa]^{<\omega}$ such that for any choice of $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$, there exists an $n<\omega$ with $G\subseteq F(A_n,A_{n+1},n+1)$.
  % \end{lemma}

  % \begin{proof}
  %   Let $\Lim([\kappa]^\omega)\subseteq[\kappa]^\omega$ denote the countable subsets of $\kappa$ for which if a set contains $\alpha+n$, then it contains $\alpha+m$ for all $m<\omega$.

  %   Let $e:[\kappa]^{<\omega}\to\kappa$ be a bijection such that for every $A\in\Lim([\kappa]^\omega)$, $e\rest [A]^{<\omega}:[A]^{<\omega}\to A$ is a bijection.

  %   Then for $A,B\in\Lim([\kappa]^\omega)$ let $F(A,B,n+1)$ contain all $G\in[B]^{<\omega}$ satsifying $f_{B}(e(G))\leq n$, and also contain all $G\in[A\cap B]^{<\omega}$ satisfying $f_{A}(e(G))\not= f_{B}(e(G))$.

  %   Fix arbitrary $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$.
  % \end{proof}

  % \begin{theorem}
  %   $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
  % \end{theorem}

  % \begin{proof}
  %   Let $f_A$ witness $S(\kappa,\omega,\omega)$ for each $A<[\kappa]^{\omega}$.

  %   Let $R(A)=\kappa^\sharp\setminus(A\times\oneptlind\kappa)$. Let $U(\gamma,A)=\{\gamma\}\times(\oneptlind{\kappa}\setminus A)$. Then note that every open cover has a pairwise disjoint open refinement of the form 
  %     \[
  %       \mc U_A = 
  %       \{R(A)\}\cup\{U(\gamma,A):\gamma\in A\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta\in A\}
  %     \]
  %   Assume without loss of generality that all covers are of the form $\mc U_A$.

  %   % Rough idea: Let $\mc U_\alpha$ cover...

  %   % Let $\sigma(\mc U,\mc V,n+1)$ be a $2$-mark.

  %   % Let $F(\alpha_n,\alpha_{n+1},n+1) = \{\alpha<\alpha_n\cap\alpha_{n+1}:\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ covers $(\alpha,\beta)$ or $(\beta,\alpha)$ for some $\beta\}$.

  %   % Claim: It is not true that for all $\alpha,\beta<\alpha_0<\alpha_1<\dots$ there exists $n<\omega$ with $\alpha,\beta\in F(\alpha_n,\alpha_{n+1},n+1)$.

  %   % If so, then choose $\alpha,\beta<\alpha_0<\alpha_1<\dots$ such that $\alpha,\beta\not\in\bigcap_{n<\omega}F(\alpha_n,\alpha_{n+1},n+1)$. Then $\sigma$ covers neither $(\alpha,\beta)$ or $(\beta,\alpha)$ in response to the attack $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$
  % \end{proof}

@@

  % Probably no good.
  % \begin{definition}
  %   A $\gamma$-cover $\mc U$ of $X$ is a countable cover such that each $x\in X$ is contained in all but finite members of $\mc U$.

  %   A $\gamma_\infty$-cover is an infinite $\gamma$-cover. 
  % \end{definition}

  % \begin{definition}
  %   A space $X$ is \textbf{Hurewicz} if and only if for each sequence $\mc U_n$ of $\gamma_\infty$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover, or $\mc F_N$ is a cover for some $N$.
  % \end{definition}

  % \begin{proposition}
  %   A space $X$ is Hurewicz if and only if for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover.
  % \end{proposition}

  % \begin{proof}
  %   Suppose $X$ is Hurewicz. For each sequence $\mc U_n$ of $\gamma$-covers, either:
  %     \begin{itemize}
  %       \item Each $\mc U_n$ is a $\gamma_\infty$-cover as well. Apply Hurewicz to find $\mc F_n$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover (and thus a $\gamma$-cover) or else $\mc F_N$ is a cover for some $N$, so letting $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N'=\mc F_N$ yields the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n'=\mc F_n$.
  %       \item Some $U_N$ is not a $\gamma_\infty$-cover as it is finite. Let $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N=\mc U_N$ to yield the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n=\mc U_n$.
  %     \end{itemize}

  %   Suppose for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover. Then for each sequence $\mc U_n$ of $\gamma_\infty$-covers, let $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover. We are now done, unless $\bigcup_{n<\omega} \mc F_n$ is finite.
  % \end{proof}

@@

\end{document}

>>>>

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\chapter{Menger Game}

Results pertaining to the Menger game characterizing the Menger property.

\section{cut-and-paste}

@@

@@

@@

@@
